% !TeX encoding = UTF-8
% !TeX program = XeLaTeX
% !TeX spellcheck = LaTeX

\documentclass[a4paper]{article}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{geometry}
\usepackage{ntheorem}
\usepackage{hyperref}
\usepackage[ruled]{algorithm2e}
\usepackage{caption,subcaption}
%\usepackage{graphicx}

\geometry{left=2cm,right=2cm,top=2cm,bottom=2cm}

\def\UrlBreaks{\do\A\do\B\do\C\do\D\do\E\do\F\do\G\do\H\do\I\do\J\do\K\do\L\do\M\do\N\do\O\do\P\do\Q\do\R\do\S\do\T\do\U\do\V\do\W\do\X\do\Y\do\Z\do\[\do\\\do\]\do\^\do\_\do\`\do\a\do\b\do\c\do\d\do\e\do\f\do\g\do\h\do\i\do\j\do\k\do\l\do\m\do\n\do\o\do\p\do\q\do\r\do\s\do\t\do\u\do\v\do\w\do\x\do\y\do\z\do\0\do\1\do\2\do\3\do\4\do\5\do\6\do\7\do\8\do\9\do\.\do\@\do\\\do\/\do\!\do\_\do\|\do\;\do\>\do\]\do\)\do\,\do\?\do\'\do+\do\=\do\#}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{claim}{Claim}
\newtheorem{conjecture}{conjecture}
\newtheorem{definition}{Definition}
\newtheorem{construction}{Construction}
\newtheorem*{proof}{Proof}
\newtheorem*{answer}{Answer}
\newtheorem*{refute}{Refute}
\newtheorem*{example}{Example}
\newtheorem*{counterexample}{Counterexample}

\newenvironment{exercise}[1]{
	\par
	\noindent\textbf{Exercise #1.}\quad
}{
	\par
	\bigskip
}


\DeclareMathAccent{\widehat}{\mathord}{largesymbols}{"62}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\pbra}[1]{\left( #1 \right)}
\newcommand{\cbra}[1]{\left\{ #1 \right\}}
\newcommand{\sbra}[1]{\left[ #1 \right]}
\newcommand{\bin}{\{0,1\}}

\title{Exercise Set --- Chapter $6$}
\date{}

\begin{document}

\maketitle



\begin{exercise}{6.1}
    \begin{itemize}
    \item Logspace-uniform circuits $\subseteq$ $\mathbf{P}$-uniform circuits $=$ $\mathbf{P}$.
    \item It is possible to simulate every TM $M$ with an oblivious TM $M'$ such that $f(n,i,j)$, which represents the position
        on $n$-length input in the $i$-th tape after $j$ steps, can be computed in logarithmic space.
            Thus the construction in Theorem 6.6 can be logspace, and $\mathbf{P}$ $\subseteq$ Logspace-uniform circuits.
    \end{itemize}
\end{exercise}

\begin{exercise}{6.1} \hspace{-1em}(Solution version 2 by Liu)

    (a) From the recursion relation:
        \begin{equation}
            f(x_1,x_2,...,x_n)=
            \begin{cases}
            f(x_1,x_2,...,x_{n-1},1) & \text{$x_n=1$}\\
            f(x_1,x_2,...,x_{n-1},0) & \text{$x_n=0$}\\
            \end{cases}
        \end{equation}
        so $f(x_1,x_2,...,x_n)=[f(x_1,x_2,...,x_{n-1},1)\wedge x_n]\vee [f(x_1,x_2,...,x_{n-1},0)\wedge \bar{x_n}]$,
        
        then we can get the relation about circle size:
         $C(n)= 2C(n-1)+5$ and $C(0)=1$.
         the solution is $C(n)=6\cdot2^{n}-5 < 10\cdot 2^{n}$.
         
    (b) There only $2^{2^{k}}$functions on k bits,so we can use $2^{2^{k}}\cdot (k 2^{k})$ gates to compute every possible  such function on $x_1,...,x_k$.Then for getting the $x_1,...x_n$,we do $n-k$ times recurion which is in (a).
    
        Then $C(n)=2^{2^{k}}\cdot (k2^{k}) + 5\cdot 2^{n-k}$.
        Make $k=log^n-2$ then $C(n)\leq 1000\cdot 2^n /n$.       
\end{exercise}

\begin{exercise}{6.4}
Prove a language has logspace-uniform circuits of polynomial size iff it is in P.

    The proof is similar to Theorem 6.6 ($P \subseteq P_{/poly}$).

\begin{itemize}
\item $\Rightarrow$  If $L$ has logspace-uniform circuit of $s$ size, then we can gain $size(n), type(n,i)$ and $edge(n,i,j)$, then we can compute the results of the circuit with poly$(s)$ time, i.e., $L \in P$.

\item $\Leftarrow$ Since $L$ can be simulated by an TM M in time $T(n)$ (in poly($n$)), then M can be simulated by an oblivious TM $M'$, which runs in time $T(n)^{2}$. Since  the snapshot $z_{i}$ is only related to time $T$ and $z_{i-1}$, thus we can compute $z_{i}$ in constant-sized circuit, then we have a $O(T(n))$ size circuit to compute L, and the circuit is logspace-uniform.
\end{itemize}
\end{exercise}

\begin{exercise}{6.5}
    Define $L$ as
    \begin{align*}
        L=\Big\{x\Big|
        &\exists C_1,|C_1|<|x|^{k+2},\\
        &\forall C_2,|C_2|<|x|^{k+1},\\
        &\exists u\in\bin^{|x|},C_1(u)\neq C_2(u),\\
        &\forall C_3,C_3<C_1 (\text{compare as binary string}),\\
        &\exists C_4,|C_4|<|x|^{k+1},\\
        &\forall v\in\bin^{|x|},C_3(v)=C_4(v),\\
        &C_1\text{ accepts }x\Big\}
    \end{align*}
    By Nonuniform Hierarchy Theorem, $\text{SIZE}(n^{k+2})\subsetneq\text{SIZE}(n^{k+1})\subsetneq\text{SIZE}(n^k)$.
    Thus $C_1$ accepts the first language which can not be accepted by circuit of size $|x|^{k+1}$, which means
    $L\notin\text{SIZE}(n^k)$ and obviously $L\in\textbf{PH}$.
\end{exercise}


\begin{exercise}{6.6}
    According to Theorem 6.19, if $\textbf{NP} \subseteq \textbf{P}_{\textbf{/poly}}$, then $\textbf{PH} = \mathbf{\Sigma}_2^p$. Thus, the conclusion of Exercise 6.5 also holds with $\mathbf{PH}$ replaced by $\mathbf{\Sigma}_2^p$. Otherwise, there exists $L \in \textbf{NP}$ such that $L \not\in \textbf{P}_{\textbf{/poly}}$. Namely, the circuit complexity is $\Omega(n^k)$ for any constant $k$.
\end{exercise}


\begin{exercise}{6.13}
\begin{itemize}
\item $\textbf{NC}^1 \subseteq formula$: copy the nodes  whose out-degree larger than $1$ and all its ancient nodes, then connect to its original neighbours. Repeat until the out-degree of each node is not larger than $1$. The depth is $O(\log n)$, so the number of nodes after above operations is $poly(n)$.
\item $ formula \subseteq\textbf{NC}^1$: the circuit is a tree $T$. Choose a sub-tree $T'$ whose nodes is more than $n/3$ and is less than $2/3$, denote the root of $T'$ as $v$.
We have $T\equiv((T-T'+\{v=true\})\wedge T')\vee((T-T'+\{v=false\})\wedge \neg T')$, so the depth $d(n)\le d(2n/3)+3$, hence $d(n)=O(\log n)$
\end{itemize}
\end{exercise}

\begin{exercise}{6.14}
\textbf{Note:} Here $NC^1$ refers to log-space uniform $NC^1$, otherwise it will contain undecidable language such as $U_B=\{1^n\quad | \exists <M,x>, |<M,x>|=n, M\text{halts on input x}\}$.

\textbf{Proof:} To prove $NC^1\subset L$, it suffice to show that we can evaluate a $O(\log n)$ depth, $poly(n)$ size circuits $\mathcal{C}_n$ by using $O(\log n)$ space. The circuit is presented by the adjacent table of its nodes. Specifically, the following 3 functions can be calculated by a $\log$-space Turing machine.
\begin{itemize}
\item[(1)] Size(n): Size of $\mathcal{C}_n$.
\item[(2)] Type(n,i): the type of $i-th$ node in $\mathcal{C}_n$.
\item[(3)] Neighbour(n,i): The left child, right child, father of the $i$-th node.
\end{itemize} 
We give the evaluation algorithm in the following box, which takes the root(the output node) as input and return   
the evaluation result, using $\log n$ space. 

\begin{algorithm}[h!]
\caption{Log-Space Algorithm for Evaluating $NC^1$}
\KwData{Root of the circuit.}
\KwResult{Output of the circuit.}
p=root \# Current node\;
q=None \# Last visited node\;
s=stack() \# Store the intermediate value in the evaluation\;
\While{p.type!="Input"}{\# p.type: "Input";"And","OR"\;
p=p.left\;}
s.push(p.val)\;
\While{!s.empty()}{p=p.father\;
\If{p==None}{return s.top() \#Completed the evaluation \;}
\If{p.right.type=="Input" or P.right==q}
{\If{p.right.type=="Input"}{
s.push(p.right.val)\;
}
temp1=s.top()\;
s.pop()\;
temp2=s.top()\;
s.pop()\;
s.push(Eval(p.type,temp1,temp2))\;
q=p \# Update the last visited node\;
}
\Else{
\While{p.type!="Input"}{p=p.left\;
}
s.push(p.val)\;
}
}
\end{algorithm}


    The algorithm is a modification of the Non-recursive post-order traversal. In the Non-recursive post-order traversal, the stack is used to record the unvisited nodes, thus takes $O(\log n\times\log n)$ spaces(record one node needs $\log |\mathcal{C}_n|=O(\log n)$ bit). We circumvent this cost by using the information of the father of a node. Instead, we use the stack to store the intermediate value in the computation. In every layer, there are at least one intermediate value. Thus the maximum usage of the stack is the depth, $O(\log n)$. The total space cost is $p,q,s$, $2\log n+|s|=O(\log n)$.
\end{exercise}

\begin{exercise}{6.15}
    (1) If $P=NC$ ,then $L\in P$ $\rightarrow$ $L \in NC$.
    
    (2) If $L$ is $P$-complete and $L \in NC$ , then $P\subseteq NC$.
        And beacuse $NC\subseteq P$,then $P=NC$.
\end{exercise}

\begin{exercise}{6.19}
    Assume \textbf{LP} has fast parallel algorithm, i.e., 
    $\textbf{LP}\in\textbf{NC}$, to show $\textbf{P}=\textbf{NC}$, it suffices
    to show \textbf{LP} is $\textbf{P}$-complete. Since $\textbf{LP}\in\textbf{P}$, we prove CIRCUIT-EVAL can be
    reduced to it in logspace. Also, $a\land b=\neg(\neg a\lor\neg b)$ and this transformation is locally computable,
    we assume the circuit contains only $\lor,\neg$.

    On the other hand,
    \begin{align*}
        x_3&=x_1\lor x_2\iff\begin{cases}
            x_3\geq x_1\\
            x_3\geq x_2\\
            x_3\leq x_1+x_2\\
            x_3\leq 1
        \end{cases}\\
        x_2&=\neg x_1\iff\begin{cases}
            x_2\geq 1-x_1\\
            x_2\leq 1-x_1
        \end{cases},
    \end{align*}
    thus the reduction is also locally computable and \textbf{LP} is then \textbf{P}-complete.
\end{exercise}

\end{document}
